---
title: "STAT 307 FINAL KNN"
author: "Bart Ryczek"
date: '2022-11-23'
output: pdf_document
---
#Factorial Anova

```{r}
Political...Factorial.Set <- read.csv("C:/Users/Bart/Downloads/Political - Factorial Set.csv")
library(agricolae)
library(MASS)
library(car)
library(rcompanion)
library(glmnet)
```

```{r}
year1MF <-c(61.42857143, 65.00, 58.57, 38.57, 37.14, 34.29)
year2MF <-c(49.29, 59.29, 67.85714286, 50.71, 55.71, 61.43)
year3MF <-c(85.00, 72.14, 82.14, 33.57, 51.43, 47.86)
year4MF <-c(65.71, 68.57, 66.43, 59.29, 35.71, 44.29)
yearGMF <-c(45.71, 57.14, 58.57, 51.43, 47.14, 45.71)


#ordering into row
y <- c(year1MF, year2MF, year3MF, year4MF, yearGMF)
y

#treatment sex
treatmentsex <- as.factor(rep(1:2, each= 3, time=5))
treatmentsex

#treatment year
treatmentyr <- as.factor(rep(1:5, each= 6))
treatmentyr


#glimpse
par(mfrow=c(1,2)) # A 1 by 2 panel of plots
boxplot(y~treatmentsex, xlab="sex")
boxplot(y~treatmentyr, xlab="year")

#glimpse 2
dataq <- data.frame(y, treatmentsex,treatmentyr)

interaction.plot(treatmentsex,treatmentyr,y)
interaction.plot(treatmentyr,treatmentsex,y)


#anova
g <- lm(y~(treatmentsex*treatmentyr))
anova(g)


#assumptions
shapiro.test(g$residuals)

#homoscedasticity
#ggaov<-aov(y~treatmentsex*treatmentyr)
bartlett.test(ggaov$residuals~treatmentsex)
bartlett.test(ggaov$residuals~treatmentyr)

#model diagnostic
#plot(g)

#subsetting for levels of method lvl 1 = 1
#small<-subset(dataq,dataq$treatmentsex==1)
#TukeyHSD(aov(small$y~small$treatmentyr), conf.level=0.95)

#subsetting for levels of method lvl 1 = 2
#small2<-subset(dataq,dataq$treatmentsex==2)
#TukeyHSD(aov(small2$y~small2$treatmentyr), conf.level=0.95)
```
#NEW CODE
```{r}
data<-read.csv("C:/Users/Bart/Downloads/Political - KNN Set.csv")
head(data)


#under repeated sampling interaction was not significant as many times as the 
#sex 
set.seed(2000)

sample(1:10, replace=FALSE)
trt = c("M1","M2","M3","M4","MG","F1","F2","F3","F4","FG")

m1<-data[sample(which(data$SEX=="Male"&data$YEAR==0),3),]
m2<-data[sample(which(data$SEX=="Male"&data$YEAR==1),3),]
m3<-data[sample(which(data$SEX=="Male"&data$YEAR==2),3),]
m4<-data[sample(which(data$SEX=="Male"&data$YEAR==3),3),]
mg<-data[sample(which(data$SEX=="Male"&data$YEAR==4),3),]

f1<-data[sample(which(data$SEX=="Female"&data$YEAR==0),3),]
f2<-data[sample(which(data$SEX=="Female"&data$YEAR==1),3),]
f3<-data[sample(which(data$SEX=="Female"&data$YEAR==2),3),]
f4<-data[sample(which(data$SEX=="Female"&data$YEAR==3),3),]
fg<-data[sample(which(data$SEX=="Female"&data$YEAR==4),3),]

table<-rbind(m1,f1,m2,f2,m3,f3,m4,f4,mg,fg)

table$SEX <- as.factor(table$SEX)

model<-lm(SCORE~as.factor(YEAR)*as.factor(SEX),data=table)
anova(model)


model<-lm(SCORE~as.factor(YEAR)+A*SEX,data=table)
anova(model)


TukeyHSD(aov(data$SCORE~data$SEX), conf.level=0.95)




interaction.plot(data$SEX,data$YEAR,data$SCORE)
interaction.plot(data$YEAR,data$SEX,data$SCORE)




shapiro.test(model$residuals)

ggaov <- aov(SCORE ~ data$YEAR * data$SEX, data=data)
#homoscedasticity
bartlett.test(ggaov$residuals~data$YEAR)
bartlett.test(ggaov$residuals~data$SEX)




#subsetting for female first
#small<-subset(data,data$SEX=="Female")
#TukeyHSD(aov(small$SCORE~as.factor(small$YEAR)), conf.level=0.95)

#subsetting for male second
#small<-subset(data,data$SEX=="Male")
#TukeyHSD(aov(small$SCORE~as.factor(small$YEAR)), conf.level=0.95)






#subsetting for female first
small<-subset(data,data$YEAR==1)
TukeyHSD(aov(small$SCORE~as.factor(small$SEX)), conf.level=0.95)

#subsetting for male second
small<-subset(data,data$YEAR==2)
TukeyHSD(aov(small$SCORE~as.factor(small$SEX)), conf.level=0.95)

#subsetting for male second
small<-subset(data,data$YEAR==3)
TukeyHSD(aov(small$SCORE~as.factor(small$SEX)), conf.level=0.95)

#subsetting for male second
small<-subset(data,data$YEAR==4)
TukeyHSD(aov(small$SCORE~as.factor(small$SEX)), conf.level=0.95)

#subsetting for male second
small<-subset(data,data$YEAR==0)
TukeyHSD(aov(small$SCORE~as.factor(small$SEX)), conf.level=0.95)

mat_dat <- as.matrix(data)

###OLD CODE BELOW ###
#table<-rbind(m1,f1,m2,f2,m3,f3,m4,f4,mg,fg)
#model<-lm(score~as.factor(year)*as.factor(sex),data=table)
#anova(model)

#shapiro.test(model$residuals)
#qqnorm(model$residuals)
#qqline(model$residuals)

#bartlett.test(model$residuals~table$year)
#bartlett.test(model$residuals~table$sex)
#plot(as.factor(table$year),model$residuals)
#plot(as.factor(table$sex),model$residuals)
```



#USING VALIDATION SET APPROACH
```{r}
PoliticalKNN <- read.csv("C:/Users/Bart/Downloads/Political - KNN Set.csv")


Elite <- rep("No", nrow(PoliticalKNN))
Elite[PoliticalKNN$SCORE > 52] <- "Yes"
Elite <- as.factor(Elite)
PoliticalKNN <- data.frame(PoliticalKNN, Elite)


#PoliticalKNN <- subset(PoliticalKNN, select=c( A,I,WB,T,TV,FU,MNS,R,B,TM,FR,P,GO,LG,GPA,SEX,YEAR,Elite))

PoliticalKNN$SEX<-ifelse(PoliticalKNN$SEX=="Male",1,0)



PoliticalKNN$SEX <- as.factor(PoliticalKNN$SEX)
PoliticalKNN$YEAR <- as.factor(PoliticalKNN$YEAR)
#PoliticalKNN$A <- as.factor(PoliticalKNN$A)
#PoliticalKNN$I <- as.factor(PoliticalKNN$I)
#PoliticalKNN$WB <- as.factor(PoliticalKNN$WB)
#PoliticalKNN$T <- as.factor(PoliticalKNN$T)
#PoliticalKNN$TV <- as.factor(PoliticalKNN$TV)
#PoliticalKNN$FU <- as.factor(PoliticalKNN$FU)
#PoliticalKNN$MNS <- as.factor(PoliticalKNN$MNS)
#PoliticalKNN$R <- as.factor(PoliticalKNN$R)
#PoliticalKNN$B <- as.factor(PoliticalKNN$B)
#PoliticalKNN$TM <- as.factor(PoliticalKNN$TM)
#PoliticalKNN$FR <- as.factor(PoliticalKNN$FR)
#PoliticalKNN$P <- as.factor(PoliticalKNN$P)
#PoliticalKNN$GO <- as.factor(PoliticalKNN$GO)
#PoliticalKNN$LG <- as.factor(PoliticalKNN$LG)
PoliticalKNN$LOCATION <- as.factor(PoliticalKNN$LOCATION)
PoliticalKNN$MAJOR <- as.factor(PoliticalKNN$MAJOR)


#PoliticalKNN$LOCATION <- as.factor(PoliticalKNN$LOCATION)

#PoliticalKNN$MAJOR <- as.factor(PoliticalKNN$MAJOR)
```

Note:
Abortion = A
Immigration = I
Welfare Benefits = WB
Tax = T
Traditional values = TV
Family unit = FU
Military and national sec= MNS
Religion = R
Business = B
Traditional Marriage = TM
Fiscal Responsability = FR
Patriotism = P
Gun ownership = GO
Limited Government = LG
_______________________________

Year in school  = Year

First - 0
Second - 1
Third - 2
Fourth - 3
Grad - 4

_______________________________
Sex = SEX
Male - 1 
Female - 0
#DONE IN R NOT INHERENT TO CSV FILE


_______________________________

Where they lived = LOCATION
0 - midwest
1 - West
2 - northeast
3 - south
4 - outside US

_______________________________
Major 
STEM - 0
Social Sciences - 1
Business - 2
Arts - 3

Unique combinations listed with own levels:

STEM BUSINESS - 4
STEM ART - 5
STEM SOC - 6
BUSINESS SOC - 7

_______________________________
Score = SCORE
Buckets of score set at median

Grades = GPA, continous






##Variable selection
```{r}
#should we scale this data?
#Poli2 <- subset(Poli2, select = -c(SCORE))
PoliticalKNN$GPA <- as.data.frame(scale(PoliticalKNN$GPA))
PoliticalKNN$GPA <- unlist(PoliticalKNN$GPA)



x <- model.matrix(SCORE ~ GPA + SEX + YEAR + LOCATION+MAJOR+A:SEX+WB:SEX+TV:SEX+MNS:SEX+R:SEX+TM:SEX+P:SEX+GO:SEX + LG:SEX + LG:YEAR, PoliticalKNN)
y <- PoliticalKNN$SCORE


grid <- 10^ seq(10, -2, length = 100)



lasso.mod <- glmnet(x, y, alpha = 1,
lambda = grid)

plot(lasso.mod)

#shall now compute cross validation and compute test error
cv.out <- cv.glmnet(x, y, alpha=1)
plot(cv.out)
bestlam <- cv.out$lambda.min




#lasso.pred <- predict(lasso.mod, s = bestlam, newx = x[test, ])
#mean((lasso.pred - y.test)^2)

#look to see our model after lasso

out <- glmnet(x, y, alpha = 1, lambda = bestlam)
lasso.coef <- predict(out, type = "coefficients",s = bestlam)
lasso.coef


newmod <- lm(y~PoliticalKNN$GPA+PoliticalKNN$LOCATION*PoliticalKNN$LG+)
```



##correlation division for SEX
```{r}
#create matrix for whichever factors you want to check

#results:Sex and abortion are correlated -> Cramer V of 0.6783 which is the alternate r^2 value

sub1 <- subset(PoliticalKNN$LG,PoliticalKNN$SEX == "1")
sub2 <- subset(PoliticalKNN$LG,PoliticalKNN$SEX == "0")

#issue as other cors dont treat these as categorical, and carmer V is issue as the data is uneven

length(sub1[sub1==10])
length(sub1[sub1==20])
length(sub1[sub1==30])
length(sub1[sub1==40])
length(sub1[sub1==50])
length(sub1[sub1==60])
length(sub1[sub1==70])
length(sub1[sub1==80])
length(sub1[sub1==90])
length(sub1[sub1==100])

man1 <- sum(length(sub1[sub1==10]), length(sub1[sub1==20]), length(sub1[sub1==30]))
man2 <- sum(length(sub1[sub1==40]), length(sub1[sub1==50]), length(sub1[sub1==60]), length(sub1[sub1==70]))
man3 <- sum(length(sub1[sub1==80]), length(sub1[sub1==90]), length(sub1[sub1==100]))

length(sub2[sub2==10])
length(sub2[sub2==20])
length(sub2[sub2==30])
length(sub2[sub2==40])
length(sub2[sub2==50])
length(sub2[sub2==60])
length(sub2[sub2==70])
length(sub2[sub2==80])
length(sub2[sub2==90])
length(sub2[sub2==100])

woman1 <- sum(length(sub2[sub2==10]), length(sub2[sub2==20]), length(sub2[sub2==30]))
woman2 <- sum(length(sub2[sub2==40]), length(sub2[sub2==50]), length(sub2[sub2==60]), length(sub2[sub2==70]))
woman3 <- sum(length(sub2[sub2==80]), length(sub2[sub2==90]), length(sub2[sub2==100]))

man <- c(man1, man2, man3)
women <-c(woman1, woman2, woman3)


data2 <- rbind(man, women)

#view table
data2

#calculate Cramer's V
cramer5<-cramerV(data2)

cramer5

#list of cramer V scores
#can include sex and abortion interaction -> cramer V .5663
#not i ->   0.2503 
#maybe include sex and wb -> 0.4576
#not t -> 0.1266 
#maybe tv -> 0.3914
#FU -> 0.2025
#MNS -> 0.3722 
#R -> 0.3418 
#B -> 0.3836
#tm -> 0.2553
#fr -> 0.1045
#p -> 0.4315
#go -> 0.4123 
#lg -> 0.213
```


##correlation division for LOCATION
```{r}

#Where they lived = LOCATION
#0 - midwest
#1 - West
#2 - northeast
#3 - south
#4 - outside US

sub1 <- subset(PoliticalKNN$GO,PoliticalKNN$LOCATION == "0")
sub2 <- subset(PoliticalKNN$GO,PoliticalKNN$LOCATION == "1")
sub3 <- subset(PoliticalKNN$GO,PoliticalKNN$LOCATION == "2")
sub4 <- subset(PoliticalKNN$GO,PoliticalKNN$LOCATION == "4")



length(sub1[sub1==10])
length(sub1[sub1==20])
length(sub1[sub1==30])
length(sub1[sub1==40])
length(sub1[sub1==50])
length(sub1[sub1==60])
length(sub1[sub1==70])
length(sub1[sub1==80])
length(sub1[sub1==90])
length(sub1[sub1==100])

midwest1 <- sum(length(sub1[sub1==10]), length(sub1[sub1==20]), length(sub1[sub1==30]))
midwest2 <- sum(length(sub1[sub1==40]), length(sub1[sub1==50]), length(sub1[sub1==60]), length(sub1[sub1==70]))
midwest3 <- sum(length(sub1[sub1==80]), length(sub1[sub1==90]), length(sub1[sub1==100]))

length(sub2[sub2==10])
length(sub2[sub2==20])
length(sub2[sub2==30])
length(sub2[sub2==40])
length(sub2[sub2==50])
length(sub2[sub2==60])
length(sub2[sub2==70])
length(sub2[sub2==80])
length(sub2[sub2==90])
length(sub2[sub2==100])

west1 <- sum(length(sub2[sub2==10]), length(sub2[sub2==20]), length(sub2[sub2==30]))
west2 <- sum(length(sub2[sub2==40]), length(sub2[sub2==50]), length(sub2[sub2==60]), length(sub2[sub2==70]))
west3 <- sum(length(sub2[sub2==80]), length(sub2[sub2==90]), length(sub2[sub2==100]))


length(sub3[sub3==10])
length(sub3[sub3==20])
length(sub3[sub3==30])
length(sub3[sub3==40])
length(sub3[sub3==50])
length(sub3[sub3==60])
length(sub3[sub3==70])
length(sub3[sub3==80])
length(sub3[sub3==90])
length(sub3[sub3==100])

northeast1 <- sum(length(sub3[sub3==10]), length(sub3[sub3==20]), length(sub3[sub3==30]))
northeast2 <- sum(length(sub3[sub3==40]), length(sub3[sub3==50]), length(sub3[sub3==60]), length(sub3[sub3==70]))
northeast3 <- sum(length(sub3[sub3==80]), length(sub3[sub3==90]), length(sub3[sub3==100]))



length(sub4[sub4==10])
length(sub4[sub4==20])
length(sub4[sub4==30])
length(sub4[sub4==40])
length(sub4[sub4==50])
length(sub4[sub4==60])
length(sub4[sub4==70])
length(sub4[sub4==80])
length(sub4[sub4==90])
length(sub4[sub4==100])

outside1 <- sum(length(sub4[sub4==10]), length(sub4[sub4==20]), length(sub4[sub4==30]))
outside2 <- sum(length(sub4[sub4==40]), length(sub4[sub4==50]), length(sub4[sub4==60]), length(sub4[sub4==70]))
outside3 <- sum(length(sub4[sub4==80]), length(sub4[sub4==90]), length(sub4[sub4==100]))




midwest <- c(midwest1, midwest2, midwest3)
west <-c(west1, west2, west3)
northeast <-c(northeast1, northeast2, northeast3)
outside <-c(outside1, outside2, outside3)


data531 <- rbind(midwest, west, northeast, outside)

#view table
data531

#calculate Cramer's V
cramer123<-cramerV(data531)

cramer123


#a - >0.1699
#i ->  0.1711 
#wb -> 0.1286 
#T -> 0.2203
#TV -> 0.2954
#FU ->0.1665
#MNS ->0.2415 
#R -> 0.1917 
#B -> 0.1297
#TM -> 0.1712 
#FR -> 0.2393
#P -> 0.234
#GO -> 0.2098 
#lg -> 0.3271
```


##correlation division for YEAR
```{r}
sub1 <- subset(PoliticalKNN$LG,PoliticalKNN$YEAR == 0)
sub2 <- subset(PoliticalKNN$LG,PoliticalKNN$YEAR == 1)
sub3 <- subset(PoliticalKNN$LG,PoliticalKNN$YEAR == 2)
sub4 <- subset(PoliticalKNN$LG,PoliticalKNN$YEAR == 3)
sub5 <- subset(PoliticalKNN$LG,PoliticalKNN$YEAR == 4)


length(sub1[sub1==10])
length(sub1[sub1==20])
length(sub1[sub1==30])
length(sub1[sub1==40])
length(sub1[sub1==50])
length(sub1[sub1==60])
length(sub1[sub1==70])
length(sub1[sub1==80])
length(sub1[sub1==90])
length(sub1[sub1==100])

fresh1 <- sum(length(sub1[sub1==10]), length(sub1[sub1==20]), length(sub1[sub1==30]))
fresh2 <- sum(length(sub1[sub1==40]), length(sub1[sub1==50]), length(sub1[sub1==60]), length(sub1[sub1==70]))
fresh3 <- sum(length(sub1[sub1==80]), length(sub1[sub1==90]), length(sub1[sub1==100]))

length(sub2[sub2==10])
length(sub2[sub2==20])
length(sub2[sub2==30])
length(sub2[sub2==40])
length(sub2[sub2==50])
length(sub2[sub2==60])
length(sub2[sub2==70])
length(sub2[sub2==80])
length(sub2[sub2==90])
length(sub2[sub2==100])

soph1 <- sum(length(sub2[sub2==10]), length(sub2[sub2==20]), length(sub2[sub2==30]))
soph2 <- sum(length(sub2[sub2==40]), length(sub2[sub2==50]), length(sub2[sub2==60]), length(sub2[sub2==70]))
soph3 <- sum(length(sub2[sub2==80]), length(sub2[sub2==90]), length(sub2[sub2==100]))


length(sub3[sub3==10])
length(sub3[sub3==20])
length(sub3[sub3==30])
length(sub3[sub3==40])
length(sub3[sub3==50])
length(sub3[sub3==60])
length(sub3[sub3==70])
length(sub3[sub3==80])
length(sub3[sub3==90])
length(sub3[sub3==100])

Jun1 <- sum(length(sub3[sub3==10]), length(sub3[sub3==20]), length(sub3[sub3==30]))
Jun2 <- sum(length(sub3[sub3==40]), length(sub3[sub3==50]), length(sub3[sub3==60]), length(sub3[sub3==70]))
Jun3 <- sum(length(sub3[sub3==80]), length(sub3[sub3==90]), length(sub3[sub3==100]))



length(sub4[sub4==10])
length(sub4[sub4==20])
length(sub4[sub4==30])
length(sub4[sub4==40])
length(sub4[sub4==50])
length(sub4[sub4==60])
length(sub4[sub4==70])
length(sub4[sub4==80])
length(sub4[sub4==90])
length(sub4[sub4==100])

Sen1 <- sum(length(sub4[sub4==10]), length(sub4[sub4==20]), length(sub4[sub4==30]))
Sen2 <- sum(length(sub4[sub4==40]), length(sub4[sub4==50]), length(sub4[sub4==60]), length(sub4[sub4==70]))
Sen3 <- sum(length(sub4[sub4==80]), length(sub4[sub4==90]), length(sub4[sub4==100]))


length(sub5[sub5==10])
length(sub5[sub5==20])
length(sub5[sub5==30])
length(sub5[sub5==40])
length(sub5[sub5==50])
length(sub5[sub5==60])
length(sub5[sub5==70])
length(sub5[sub5==80])
length(sub5[sub5==90])
length(sub5[sub5==100])

grad1 <- sum(length(sub5[sub5==10]), length(sub5[sub5==20]), length(sub5[sub5==30]))
grad2 <- sum(length(sub5[sub5==40]), length(sub5[sub5==50]), length(sub5[sub5==60]), length(sub5[sub5==70]))
grad3 <- sum(length(sub5[sub5==80]), length(sub5[sub5==90]), length(sub5[sub5==100]))


fresh <- c(fresh1,fresh2,fresh3)
sophmore <- c(soph1, soph2, soph3)
junior <- c(Jun1, Jun2, Jun3)
senior <- c(Sen1, Sen2, Sen3)
graduate <-c(grad1,grad2,grad3)


data127 <- rbind(fresh, sophmore, junior, senior, graduate)

#view table
#data127

#calculate Cramer's V
cramer321<-cramerV(data127)

cramer321


#a = 0.1698
#i = 0.2011
#wb ->  0.2298 
#T -> 0.2316
#TV -> 0.2157 
#FU -> 0.1979 
#MNS -> 0.2491 
#R ->  0.2802
#B -> 0.1542 
#TM ->  0.2565 
#FR -> 0.1682
#P -> 0.2222 
#GO ->  0.2643
#lg -> 0.2546 
```


##correlation division for MAJOR
```{r}
#Major 
#STEM - 0
#Social Sciences - 1
#Business - 2
#Arts - 3
#STEM BUSINESS - 4
#STEM ART - 5
#STEM SOC - 6
#BUSINESS SOC - 7

sub1 <- subset(PoliticalKNN$LG,PoliticalKNN$MAJOR == 0)
sub2 <- subset(PoliticalKNN$LG,PoliticalKNN$MAJOR == 1)
sub3 <- subset(PoliticalKNN$LG,PoliticalKNN$MAJOR == 2)
sub4 <- subset(PoliticalKNN$LG,PoliticalKNN$MAJOR == 3)
sub5 <- subset(PoliticalKNN$LG,PoliticalKNN$MAJOR == 4)
sub6 <- subset(PoliticalKNN$LG,PoliticalKNN$MAJOR == 5)
sub7 <- subset(PoliticalKNN$LG,PoliticalKNN$MAJOR == 6)
sub8 <- subset(PoliticalKNN$LG,PoliticalKNN$MAJOR == 7)


length(sub1[sub1==10])
length(sub1[sub1==20])
length(sub1[sub1==30])
length(sub1[sub1==40])
length(sub1[sub1==50])
length(sub1[sub1==60])
length(sub1[sub1==70])
length(sub1[sub1==80])
length(sub1[sub1==90])
length(sub1[sub1==100])

fresh1 <- sum(length(sub1[sub1==10]), length(sub1[sub1==20]), length(sub1[sub1==30]))
fresh2 <- sum(length(sub1[sub1==40]), length(sub1[sub1==50]), length(sub1[sub1==60]), length(sub1[sub1==70]))
fresh3 <- sum(length(sub1[sub1==80]), length(sub1[sub1==90]), length(sub1[sub1==100]))

length(sub2[sub2==10])
length(sub2[sub2==20])
length(sub2[sub2==30])
length(sub2[sub2==40])
length(sub2[sub2==50])
length(sub2[sub2==60])
length(sub2[sub2==70])
length(sub2[sub2==80])
length(sub2[sub2==90])
length(sub2[sub2==100])

soph1 <- sum(length(sub2[sub2==10]), length(sub2[sub2==20]), length(sub2[sub2==30]))
soph2 <- sum(length(sub2[sub2==40]), length(sub2[sub2==50]), length(sub2[sub2==60]), length(sub2[sub2==70]))
soph3 <- sum(length(sub2[sub2==80]), length(sub2[sub2==90]), length(sub2[sub2==100]))


length(sub3[sub3==10])
length(sub3[sub3==20])
length(sub3[sub3==30])
length(sub3[sub3==40])
length(sub3[sub3==50])
length(sub3[sub3==60])
length(sub3[sub3==70])
length(sub3[sub3==80])
length(sub3[sub3==90])
length(sub3[sub3==100])

Jun1 <- sum(length(sub3[sub3==10]), length(sub3[sub3==20]), length(sub3[sub3==30]))
Jun2 <- sum(length(sub3[sub3==40]), length(sub3[sub3==50]), length(sub3[sub3==60]), length(sub3[sub3==70]))
Jun3 <- sum(length(sub3[sub3==80]), length(sub3[sub3==90]), length(sub3[sub3==100]))



length(sub4[sub4==10])
length(sub4[sub4==20])
length(sub4[sub4==30])
length(sub4[sub4==40])
length(sub4[sub4==50])
length(sub4[sub4==60])
length(sub4[sub4==70])
length(sub4[sub4==80])
length(sub4[sub4==90])
length(sub4[sub4==100])

Sen1 <- sum(length(sub4[sub4==10]), length(sub4[sub4==20]), length(sub4[sub4==30]))
Sen2 <- sum(length(sub4[sub4==40]), length(sub4[sub4==50]), length(sub4[sub4==60]), length(sub4[sub4==70]))
Sen3 <- sum(length(sub4[sub4==80]), length(sub4[sub4==90]), length(sub4[sub4==100]))


length(sub5[sub5==10])
length(sub5[sub5==20])
length(sub5[sub5==30])
length(sub5[sub5==40])
length(sub5[sub5==50])
length(sub5[sub5==60])
length(sub5[sub5==70])
length(sub5[sub5==80])
length(sub5[sub5==90])
length(sub5[sub5==100])

grad1 <- sum(length(sub5[sub5==10]), length(sub5[sub5==20]), length(sub5[sub5==30]))
grad2 <- sum(length(sub5[sub5==40]), length(sub5[sub5==50]), length(sub5[sub5==60]), length(sub5[sub5==70]))
grad3 <- sum(length(sub5[sub5==80]), length(sub5[sub5==90]), length(sub5[sub5==100]))

length(sub6[sub6==10])
length(sub6[sub6==20])
length(sub6[sub6==30])
length(sub6[sub6==40])
length(sub6[sub6==50])
length(sub6[sub6==60])
length(sub6[sub6==70])
length(sub6[sub6==80])
length(sub6[sub6==90])
length(sub6[sub6==100])

sb1 <- sum(length(sub6[sub6==10]), length(sub6[sub6==20]), length(sub6[sub6==30]))
sb2 <- sum(length(sub6[sub6==40]), length(sub6[sub6==50]), length(sub6[sub6==60]), length(sub6[sub6==70]))
sb3 <- sum(length(sub6[sub6==80]), length(sub6[sub6==90]), length(sub6[sub6==100]))

length(sub7[sub7==10])
length(sub7[sub7==20])
length(sub7[sub7==30])
length(sub7[sub7==40])
length(sub7[sub7==50])
length(sub7[sub7==60])
length(sub7[sub7==70])
length(sub7[sub7==80])
length(sub7[sub7==90])
length(sub7[sub7==100])

sa1 <- sum(length(sub7[sub7==10]), length(sub7[sub7==20]), length(sub7[sub7==30]))
sa2 <- sum(length(sub7[sub7==40]), length(sub7[sub7==50]), length(sub7[sub7==60]), length(sub7[sub7==70]))
sa3 <- sum(length(sub7[sub7==80]), length(sub7[sub7==90]), length(sub7[sub7==100]))

length(sub8[sub8==10])
length(sub8[sub8==20])
length(sub8[sub8==30])
length(sub8[sub8==40])
length(sub8[sub8==50])
length(sub8[sub8==60])
length(sub8[sub8==70])
length(sub8[sub8==80])
length(sub8[sub8==90])
length(sub8[sub8==100])

bs1 <- sum(length(sub8[sub8==10]), length(sub8[sub8==20]), length(sub8[sub8==30]))
bs2 <- sum(length(sub8[sub8==40]), length(sub8[sub8==50]), length(sub8[sub8==60]), length(sub8[sub8==70]))
bs3 <- sum(length(sub8[sub8==80]), length(sub8[sub8==90]), length(sub8[sub8==100]))



fresh <- c(fresh1,fresh2,fresh3)
sophmore <- c(soph1, soph2, soph3)
junior <- c(Jun1, Jun2, Jun3)
senior <- c(Sen1, Sen2, Sen3)
graduate <-c(grad1,grad2,grad3)
sb <-c(sb1,sb2,sb3)
sa <-c(sa1,sa2,sa3)
bs <-c(bs1,bs2,bs3)

data820 <- rbind(fresh, sophmore, junior, senior, graduate, sb, sa, bs)

#view table
#data127

#calculate Cramer's V
cramer3221<-cramerV(data820)

cramer3221


#a =  0.4304 
#i = 0.2691 
#wb -> 0.4254 
#T -> 0.3139 
#TV -> 0.4053
#FU ->  0.3955
#MNS ->  0.4094 
#R ->  0.3901
#B ->  0.3386
#TM ->  0.3743 
#FR -> 0.275
#P ->  0.345
#GO ->  0.4827 
#lg ->  0.3632
```

```{r}
subs1 <- subset(PoliticalKNN$A,PoliticalKNN$SEX =="1")
subs2 <- subset(PoliticalKNN$A,PoliticalKNN$SEX =="0")

gender<- c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1)

scores <- c(subs2,subs1)

cor.test(gender, scores)
```
